---
title: "BOI_Regression"
author: "Stan West"
date: "2024-10-07"
output: pdf_document
---


### This document describes the relationship between scores on the ADC and performance on a semantic decision task. Independent samples t-tests show that groups overall do not differ in accuracy or response latency *t*(603.71) = -0.56, *p* = 0.58 & *t*(597.39) = 1.49, *p* = 0.14, respectively. Distributions of response latency and accuracy across groups and BOI are shown in the violin plots below. Also plotted is the distribution of accuracy and resposne latency across a range of ADC scores. Each point refers to the average latency or average accuracy for a participant in each of the BOI levels. This is separated out by group. Finally, there are nested linear models showing the relationship between each of our DVs (resposne latency & accuracy) and group, group and BOI level, and group, BOI level, and ADC score. Nested model comparisons show that the best fitting model for both of the DVs includes group & BOI level, but not ADC scores. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(knitr)
library(svglite)

df <- readRDS("data/BOI-Assert-ADC_metadata.rds")
load("data/stim_600.Rdata")
df_stim <- conc_abs_stim %>%
  select(Word, level = level) %>%
  unique() %>%
  mutate(level = as.character(level))

df_stim$level[is.na(df_stim$level) ] <- "abstract"
df_stim$level <- as.factor(df_stim$level)



```



```{r,echo=F,error=FALSE}
df_descrip <- df %>%
  left_join(df_stim, by = c("word" = "Word")) %>%
  select(PROLIFIC_PID, correct, duration, group, n_correct,n_incorrect, level,adc_compscore) %>%
  group_by(PROLIFIC_PID, level) %>%
  summarize(PROLIFIC_PID = PROLIFIC_PID, 
            mean_duration = mean(duration),
            perc_correct = sum(correct == "true")/sum(correct == "true" | correct == "false"),
            group = as.factor(group),
            adc_compscore = adc_compscore) %>%
  unique() %>%
  ungroup


```


## Table of means and violin plots 

```{r, echo = FALSE}

x <- df_descrip %>%
  group_by(group) %>%
  summarize(mean_dur = mean(mean_duration),
            sd_dur = sd(mean_duration),
            mean_correct = mean(perc_correct),
            sd_correct = sd(perc_correct))


y <- df_descrip %>%
  group_by(group,level) %>%
  summarize(mean_dur = mean(mean_duration),
            sd_dur = sd(mean_duration),
            mean_correct = mean(perc_correct),
            sd_correct = sd(perc_correct))

adc <- df_descrip %>%
  group_by(group) %>%
  summarize(mean_adc = mean(adc_compscore),
            sd_adc = sd(adc_compscore))

kable(x, caption = "Descriptives Between Groups",col.names = c("Group", "Mean Duration","SD Duration", "Average Percent Correct", "SD Percent Correct"))
kable(y, caption = "Descriptives Between Groups and BOI Levels",col.names = c("Group","Level", "Mean Duration","SD Duration", "Average Percent Correct", "SD Percent Correct"))
kable(adc, caption = "ADC Descriptives Between Groups",col.names = c("Group", "Mean ADC","SD ADC"))



ggplot(df_descrip %>% filter(!level == "abstract"), aes(x = group, y = mean_duration, color = group))+
  scale_color_manual(values = c("#461D7C", "#D29F13"), guide = "none")+
  scale_x_discrete(labels = c("autistic","non-autistic"))+
  geom_violin(trim = FALSE)+
  labs(y = "reaction time")+
  geom_boxplot(width = 0.1, color = "#595959")+
  facet_grid(~factor(level, levels = c("low","medium", "high")))+
  ggtitle("Average Group Reaction Time Across BOI Levels")+
  theme_bw()
ggsave("Figures/reaction_time.svg",width = 7.5,height = 7)


ggplot(df_descrip %>% filter(!level == "abstract"), aes(x = group, y = mean_duration, color = group))+
  scale_color_manual(values = c("#461D7C", "#D29F13"), guide = "none")+
  scale_x_discrete(labels = c("autistic","non-autistic"))+
  geom_violin(trim = FALSE)+
  labs(y = "reaction time")+
  geom_boxplot(width = 0.1, color = "#595959")+
  facet_grid(~factor(level, levels = c("low","medium", "high")))+
  ggtitle("Average Group Reaction Time Across BOI Levels")+
  geom_point(position = "jitter", alpha = 0.3)+
  theme_bw()
ggsave("Figures/reaction_time_points.svg",width = 7.5,height = 7)




ggplot(df_descrip %>% filter(!level == "abstract"), aes(x = group, y = perc_correct, color = group))+
  scale_color_manual(values = c("#461D7C", "#D29F13"), guide = "none")+
  scale_x_discrete(labels = c("autistic","non-autistic"))+
  geom_violin(trim = FALSE)+
  labs(y = "% accuracy")+
  geom_boxplot(width = 0.1, color = "#595959")+
  facet_grid(~factor(level, levels = c("low","medium", "high")))+
  theme_bw()+
  ggtitle("Group Accuracy Across BOI Levels")
ggsave("Figures/accuracy.svg",width = 7.5,height = 7)

ggplot(df_descrip %>% filter(!level == "abstract"), aes(x = group, y = perc_correct, color = group))+
  scale_color_manual(values = c("#461D7C", "#D29F13"), guide = "none")+
  scale_x_discrete(labels = c("autistic","non-autistic"))+
  geom_violin(trim = FALSE)+
  labs(y = "% accuracy")+
  geom_boxplot(width = 0.1, color = "#595959")+
  facet_grid(~factor(level, levels = c("low","medium", "high")))+
  theme_bw()+
  geom_point(position = "jitter", alpha = 0.2)+
  ggtitle("Group Accuracy Across BOI Levels")
ggsave("Figures/accuracy_points.svg",width = 7.5,height = 7)

# HEx codes to use
#LSUPurple='#461D7C'
#LSUGold='#D29F13'


```


## T-tests of overall response latency and accuracy. Groups do not differ in overall response latency or accuracy.

```{r, echo=FALSE}
t.test(mean_duration ~ group, data = df_descrip)
t.test(perc_correct ~ group, data = df_descrip)

```


## Plotting duration and percent correct over ADC scores.

```{r, echo = FALSE}

ggplot(df_descrip, aes(x = adc_compscore, y = mean_duration, color = group))+
  geom_point(alpha = 0.5) +
  facet_grid(~level)+
  geom_smooth(method = "lm",alpha = 0.3)+
  ggtitle("Scatterplot of Average Durations Between Groups and Across BOI")


ggplot(df_descrip, aes(x = adc_compscore, y = perc_correct, color = group))+
  geom_point(alpha = 0.5) +
  facet_grid(~level)+
  geom_smooth(method = "lm", alpha = 0.3)+
  ggtitle("Scatterplot of Percent Correct Between Groups and Across BOI")

```


## Nested model comparisons (group, group + level, & group + level + ADC)

```{r}
m1_duration <- lm(mean_duration ~ group, data = df_descrip)
m2_duration <- lm(mean_duration ~ group * level, data = df_descrip)
m3_duration <- lm(mean_duration ~ group * level + adc_compscore, data = df_descrip)
list_mods_dur <- list(model_1 = m1_duration,model_2 = m2_duration,model_3 = m3_duration)
lapply(list_mods_dur, summary)

anova( m1_duration,m2_duration,m3_duration)


m1_correct <- lm(perc_correct ~ group, data = df_descrip)
m2_correct <- lm(perc_correct ~ group * level, data = df_descrip)
m3_correct <- lm(perc_correct ~ group * level + adc_compscore, data = df_descrip)
list_mods_acc <- list(model_1 = m1_correct, model_2 = m2_correct, model_3 = m3_correct)
lapply(list_mods_acc, summary)

anova(m1_correct,m2_correct,m3_correct)


```




## Nested model comparisons no abstract category (group, group + level, & group + level + ADC, with interactions)

```{r}

d_descrip_no_abstract <- df_descrip %>%
  filter(!level == "abstract") %>%
  mutate(level = droplevels(factor(level, levels = c("low", "medium", "high"), labels = c("low", "mid", "high"))))

contr.mat.level <- matrix(data = c(2,0,-1,1,-1,-1), nrow = 3, ncol = 2, byrow = T,)
colnames(contr.mat.level) <- c("mh_v_low","high_v_mid")
contr.mat.group <- matrix(data = c(-0.5,0.5), nrow = 2, ncol = 1, byrow = T,)
colnames(contr.mat.group) <- c("non-ASD")



contrasts(d_descrip_no_abstract$group) <- contr.mat.group
contrasts(d_descrip_no_abstract$level) <- contr.mat.level


m1_duration <- lm(mean_duration ~ group, data = d_descrip_no_abstract)
m2_duration <- lm(mean_duration ~ group * level, data = d_descrip_no_abstract)
m3_duration <- lm(mean_duration ~ group * level * adc_compscore, data = d_descrip_no_abstract)
list_mods_dur <- list(model_1 = m1_duration,model_2 = m2_duration,model_3 = m3_duration)
lapply(list_mods_dur, summary)

anova( m1_duration,m2_duration,m3_duration)


m1_correct <- lm(perc_correct ~ group, data = d_descrip_no_abstract)
m2_correct <- lm(perc_correct ~ group * level, data = d_descrip_no_abstract)
m3_correct <- lm(perc_correct ~ group * level * adc_compscore, data = d_descrip_no_abstract)
list_mods_acc <- list(model_1 = m1_correct, model_2 = m2_correct, model_3 = m3_correct)
lapply(list_mods_acc, summary)

anova(m1_correct,m2_correct,m3_correct)


```


